Fuzzy Extractors for Noisy Sources \\with More Errors Than Entropy

### 2015-02-11 trunk/constantRate/ConstCompFuzzExt-crypto.tex
minor edits to grammar

\begin{table}
\begin{center}
\ifnum\lncs=0
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\end{tabular}
\else
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline \vspace{-3mm} \\
Construction \ref{cons:sampling} & high-entropy & any subconstant \ \ &  Sample-then-obfuscate \\
\ \ (reusable)& \ \ samples\\ \vspace{-3mm} \\
Construction \ref{cons:first construction}  & sparse high-entropy \ \  & constant &  Error-correct-and-obfuscate\\
& \ \ marginals\\ \vspace{-3mm} \\
Construction \ref{cons:info theoretic}   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\ \ (info-theoretic)\\
\hline\end{tabular}
\fi
\end{center}
%end centering
\caption{Summary of new constructions. \consref{cons:sampling} supports the widest class of sources, including sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.  \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
\label{tab:upper bounds}
\end{table}

@@

We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with sparse high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed. In this construction, we use single symbols of $w$ for locking up bits of a secret that we then transform into $r$. This construction tolerates a higher error rate than the first construction, but over a larger alphabet, where errors may be more likely.

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols. It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies existing fuzzy extractors to the resulting string.

@@

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if 
\ifnum\lncs=0
$\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ 
\else
\[
\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy
\]
\fi
for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

@@

We first define a slightly weaker object than a computational fuzzy extractor: it outputs a key with computational entropy~(instead of a pseudorandom key).  
We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).

Before defining this object, we define conditional computational (``HILL'' \cite{DBLP:journals/siamcomp/HastadILL99}) entropy.

>>>>

\begin{table}
\begin{center}
\ifnum\lncs=0
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline
Cons. \ref{cons:sampling} (reusable)  & high-entropy samples & any subconstant &  Sample-then-obfuscate \\
Cons. \ref{cons:first construction}  & sparse high-entropy  marginals & constant &  Error-correct-and-obfuscate\\
Cons. \ref{cons:info theoretic} (info-theoretic)   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\end{tabular}
\else
\begin{tabular}{l l l l l}
  & Source Structure & Error Rate  & Techniques\\
\hline \vspace{-3mm} \\
Construction \ref{cons:sampling} & high-entropy & any subconstant \ \ &  Sample-then-obfuscate \\
\ \ (reusable)& \ \ samples\\ \vspace{-3mm} \\
Construction \ref{cons:first construction}  & sparse high-entropy \ \  & constant &  Error-correct-and-obfuscate\\
& \ \ marginals\\ \vspace{-3mm} \\
Construction \ref{cons:info theoretic}   & sparse block source  & constant & Condense-then-fuzzy-extract\\
\ \ (info-theoretic)\\
\hline\end{tabular}
\fi
\end{center}
%end centering
\caption{Summary of new constructions. \consref{cons:sampling} supports the widest class of sources, including the sources supported by the other two constructions, but tolerates fewer errors than the other two constructions.  \consref{cons:first construction} and \consref{cons:info theoretic} support incomparable classes of sources.}
\label{tab:upper bounds}
\end{table}

@@

We augment the first construction with error-correcting codes to obtain our second construction, which works for \emph{sources with sparse high-entropy marginals}: sources over large alphabets for which sufficiently many symbols have high entropy individually, but no independence among symbols is assumed. In this construction, we use single symbols of $w$ to lock up bits of a secret that we then transform into $r$. This construction tolerates a higher error rate than the first construction, but over a larger alphabet, where errors may be more likely.

Our third construction provides information-theoretic, rather than computational, security. It works for \emph{sparse block sources}. These are sources in which a sufficient fraction of the symbols have entropy conditioned on previous symbols. It uses symbol-by-symbol condensers to reduce the alphabet size while preserving most of the entropy, and then applies a standard fuzzy extractor to the resulting string.

@@

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = |\{i | x_i \neq y_i\}|$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

@@

\paragraph{Sources with High-Entropy Samples}
Let the source $W=W_1, \dots, W_\gamma$ consist of strings of length $\gamma$ over some arbitrary alphabet $\mathcal{Z}$. For some parameters $\eta, \subsetEntropy$, we say that the source $W$ is a source with  \emph{$\subsetEntropy$-entropy $\eta$-samples} if 
\ifnum\lncs=0
$\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy$ 
\else
\[
\Hav(W_{j_1}, \dots, W_{j_\eta}\, |\, j_1, \dots, j_\eta)>\subsetEntropy
\]
\fi
for uniformly random distinct $1< j_1, \dots, j_\eta \le \gamma$. \bnote{there is no probabilistic guarantee here} This property can hold, for example, if the symbols $W_i$ are $\eta$-wise independent, and each has entropy at least $\subsetEntropy/\eta$. However, that's not the only way for the property to hold: for example, we can allow sources in which some symbols have little entropy or depend on other symbols, by simply choosing a larger $\eta$ to compensate.

@@

We first define a slightly weaker object than a computational fuzzy extractor: it outputs a key with computational entropy~(instead of a pseudorandom key).  
We call this object a computational fuzzy conductor.  It is the computational analogue of a fuzzy conductor~(introduced by Kanukurthi and Reyzin~\cite{KanukurthiR09}).
Before defining this object, we define conditional computational (``HILL'' \cite{DBLP:journals/siamcomp/HastadILL99}) entropy.
